Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-03-10 manuscript.Rmd
finished results

```{r pos-correlations}
pos_sum_ppt <- map(fullday, 
                   ~ group_by(.x, age, id_uni) %>% 
                     filter(is.na(nap_time)) %>% 
                     summarize(across(sit_time:upright_time, \(x) mean(x, na.rm = TRUE))) %>% 
                     ungroup %>% select(-id_uni))

@@

Figure \@ref(fig:age) shows that both group and individual model predictions captured age-related differences in body position. Age in months and upright time were significantly, positively correlated using group (*r* = `r age_cor_group["age","upright_time"]`, *p* `r apa_p(age_cor_group_pval["age","upright_time"])`)

>>>>

```{r pos-correlations, cache=TRUE, cache.extra=tools::md5sum("data/imu-compiled.csv")}
pos_sum_ppt <- map(fullday, 
                   ~ group_by(.x, age, id_uni) %>% 
                     filter(is.na(nap_time)) %>% 
                     summarize(across(sit_time:upright_time, \(x) mean(x, na.rm = TRUE))) %>% 
                     ungroup %>% select(-id_uni))

@@

Figure \@ref(fig:age) shows that both group and individual model predictions captured age-related differences in body position. Age in months and upright time were significantly, positively correlated using group (*r* = `r age_cor_group["age","upright_time"]`, *p* `r apa_p(age_cor_group_pval["age","upright_time"], add_equals = T)`) and individual models (*r* = `r age_cor_ind["age","upright_time"]`, *p* `r apa_p(age_cor_ind_pval["age","upright_time"], add_equals = T)`). Similarly, age predicted increases in sitting time using group (*r* = `r age_cor_group["age","sit_time"]`, *p* `r apa_p(age_cor_group_pval["age","sit_time"], add_equals = T)`) and individual models (*r* = `r age_cor_ind["age","sit_time"]`, *p* `r apa_p(age_cor_ind_pval["age","sit_time"], add_equals = T)`). In contrast, age predicted decreases in supine time using group (*r* = `r age_cor_group["age","supine_time"]`, *p* `r apa_p(age_cor_group_pval["age","supine_time"], add_equals = T)`) and individual models (*r* = `r age_cor_ind["age","supine_time"]`, *p* `r apa_p(age_cor_ind_pval["age","supine_time"], add_equals = T)`). No clear age trends were found for prone time. Age was not significantly related to held time for group models (*r* = `r age_cor_group["age","held_time"]`, *p* `r apa_p(age_cor_group_pval["age","held_time"], add_equals = T)`), but individual models showed a significant negative correlation (*r* = `r age_cor_ind["age","held_time"]`, *p* `r apa_p(age_cor_ind_pval["age","held_time"], add_equals = T)`) resulting from an outlier in the younger group.

### 2023-03-10 manuscript.tex
finished results

Figure \ref{fig:age} shows that both group and individual model predictions captured age-related differences in body position. Age in months and upright time were significantly, positively correlated using group (\emph{r} = 0.59, \emph{p} \textless{} .001)

>>>>

Figure \ref{fig:age} shows that both group and individual model predictions captured age-related differences in body position. Age in months and upright time were significantly, positively correlated using group (\emph{r} = 0.59, \emph{p} \textless{} .001) and individual models (\emph{r} = 0.50, \emph{p} = .005). Similarly, age predicted increases in sitting time using group (\emph{r} = 0.70, \emph{p} \textless{} .001) and individual models (\emph{r} = 0.72, \emph{p} \textless{} .001). In contrast, age predicted decreases in supine time using group (\emph{r} = -0.66, \emph{p} \textless{} .001) and individual models (\emph{r} = -0.61, \emph{p} \textless{} .001). No clear age trends were found for prone time. Age was not significantly related to held time for group models (\emph{r} = -0.22, \emph{p} = .212), but individual models showed a significant negative correlation (\emph{r} = -0.42, \emph{p} = .021) resulting from an outlier in the younger group.
